\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Journal of International Electrical Power and Energy Systems}
%JANKCE adding


%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Electrical Power and Energy Systems\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Elsevier Latex Template template}

%% Group authors per affiliation:
\author{BG Lindner \corref{mycorrespondingauthor} \& J Eygelaar \& JH van Vuuren}
% \address{Radarweg 29, Amsterdam}
% \fntext[myfootnote]{}

%% or include affiliations in footnotes:z
% \author[mymainaddress,mysecondaryaddress]{}
% \ead[url]{www.elsevier.com}

% \author[mysecondaryaddress]{Global Customer Service}
\cortext[mycorrespondingauthor]{Department of Industrial Engineering, Stellenbosch University, Private bag X1, Matieland, 7602, South
Africa, fax: 021 8082409, email: 15150526@sun.ac.za}
% \ead{support@elsevier.com}

% \address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
% \address[mysecondaryaddress]{360 Park Avenue South, New York}

\begin{abstract}
Providing reliable energy is a major force in shaping the economic welfare of a developing country. For a power utility in such a country one of the key focus areas is the planned preventative
maintenance of the power generating units in its power system. The celebrated \textit{generator maintenance scheduling} (GMS) problem is the problem of finding a schedule
for the planned maintenance outages of generating units in a power system. 
A novel tri-objective model formulation is proposed for the GMS problem.
The first (and most commonly adopted) objective involves minimising the squared reserve levels, which serves to create an even (``reliable'') margin of generating capacity over and above expected demand. 
The second objective involves the
production cost associated with a maintenance plan for the generating units in a system, where planning maintenance on a power generating unit which is cheap to operate during a high demand period will incur 
a higher production cost. The third objective
involves the risk (on expectation) of generating units breaking down, where the longer the time period since the last maintenance service of a generating unit, the larger the risk of it breaking down.
The solutions to this GMS problem, \textit{i.e.}\ maintenance plans, may be used by decision makers within a national power utility. 
\end{abstract}

\begin{keyword}
Generator maintenance scheduling, Simulated annealing, power system, reliability
%\MSC[2010] 00-01\sep  99-00
\end{keyword}

\end{frontmatter}

\linenumbers

\section{The Elsevier article class}

\paragraph{Installation} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.

\paragraph{Usage} Once the package is properly installed, you can use the document class \emph{elsarticle} to create a manuscript. Please make sure that your manuscript follows the guidelines in the Guide for Authors of the relevant journal. It is not necessary to typeset your manuscript in exactly the same way as an article, unless you are submitting to a camera-ready copy (CRC) journal.

\paragraph{Functionality} The Elsevier article class is based on the standard article class and supports almost all of the functionality of that class. In addition, it features commands and options to format the
\begin{itemize}
\item document style
\item baselineskip
\item front matter
\item keywords and MSC codes
\item theorems, definitions and proofs
\item lables of enumerations
\item citation style and labeling.
\end{itemize}

\section{Front matter}

The author names and affiliations could be formatted in two ways:
\begin{enumerate}[(1)]
\item Group the authors per affiliation.
\item Use footnotes to indicate the affiliations.
\end{enumerate}
See the front matter of this document for examples. You are recommended to conform your choice to the journal you are submitting to.

\section{Bibliography styles}

There are various bibliography styles available. You can select the style of your choice in the preamble of this document. These styles are Elsevier styles based on standard styles like Harvard and Vancouver. Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.

Here are two sample references: \cite{Feynman1963118,Dirac1953888}.

\section*{References}

\bibliography{mybibfile}

\end{document}